---
title: "process-QT-SurveyResults"
author: "Haoran Xu"
date: "2024-11-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

I have an Excel file with data that was collected in the questionnaire during July-August on Qinghai-Tibet Plateau.

The name of the file is `QT_SurveyResults.xlsx` and it contains only one sheet:

- Energy_Emissions: the data

To make it easy to share this dataset I will read it, convert it to an `.RData` file, and then document it so that it can be bundled with package `QTSEM`.

Load the packages needed to preprocess the data:
```{r}
library(tidyverse)
library(readxl)
```

Read the Excel file as a dataframe:
```{r}
SurveyResults <- read_excel("QT_SurveyResults.xlsx")
```

The dataframe consists of 813 observations of 43 variables. Get a summary of the dataframe:
```{r}
summary(SurveyResults)
```

The sources of these data are collected with Dr. Huaxiong Jiang, Kaifei Guo and Lili Zhang on Qinghai-Tibet Plateau during July to August in 2022.

Save to data folder:
```{r}
usethis::use_data(SurveyResults,
                  overwrite = TRUE)
```
